---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hw4package

<!-- badges: start -->
<!-- badges: end -->

The goal of hw4package is to get a good grade on Professor Ressler's homework 4 assignment for STAT 613 at American University. This package accomplishes this by create two functions: one that generates random samples from 4 different distributions, and another that generates plots of histograms for random samples from 4 different distributions. 

## Installation

You can install the released version of hw4package from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("hw4package")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("kshrawder/hw4KevinShrawder/hw-04-packages-kshrawder")
```
## Usage

This is a basic example of the get_samples_dist function which returns the generated random samples from a selection of 4 different distributions. 

```{r example}
library(hw4package)
get_samples_dist('normal', 10)
```


This is a basic example of the get_plots_dist() function which returns a histogram of the generated random samples from a selection of 4 different distributions. 

```{r cars}
get_plots_dist('normal', 10, bins = 5)
```

